### 2017-10-14 Draft2.tex
Rename to funnel array

	In this section, I define \textbf{fields} and \textbf{properties} on dynamic arrays and resize lists. These will be used later to implement operations on them in pseudocode.

	\section{Common Resize List Operations}

	In this section, I implement common operations for dynamic arrays, then resize lists, in pseudocode. Then, I analyze and compare the time complexities of the implementations. If the operation allocates memory, I also compare their space complexities.

@@

	Adding is the most common operation done on a dynamic array\footnote{}. Resize lists improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.

@@

	% <resize list implementation>

@@

	\section{Other Resize List Operations}

>>>>

	In this section, I define \textbf{fields} and \textbf{properties} on dynamic and funnel arrays. These will be used later to implement operations on them in pseudocode.

	\section{Common Funnel Array Operations}

	In this section, I implement common operations for dynamic arrays, then funnel arrays, in pseudocode. Then, I analyze and compare the time complexities of the implementations. If the operation allocates memory, I also compare their space complexities.

@@

	Adding is the most common operation done on a dynamic array\footnote{}. Funnel arrays improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.

@@

	% <funnel array implementation>

@@

	\section{Other Funnel Array Operations}
